\documentclass{resume}

\rohead{\thepage\ of \pageref{LastPage}}

\cofoot{
    \begin{spacing}{1}
    \so{Boston, MA}\\
    
    \hspace{0.25cm}
    \small{\footeremail{thepaulplew@gmail.com}}
    \hspace{0.25cm}
    \small{\footerphone{+1 (310) 948-3839}}
    \hspace{0.25cm}
    \small{\footerlink{https://plew.dev}{plew.dev}}
    \end{spacing}
}

\begin{document}

\name{Paul Plew}
\smallskip

\section{Experience}

\employer
    {Alloy Enterprises}
    {https://alloyenterprises.co}
    {January 2023 --- November 2024}
    {Full Stack Software Engineer}
    {\begin{jobitems}
        \item Designed and implemented robust back-end systems to enhance functionality and improve performance of custom internal tool-path generation software written in python and c++.
        \item Developed and deployed a material quality inspection system, integrating it with the company's internal manufacturing execution system, resulting in increased manufacturing throughput and improved traceability.
        \item Built responsive, user-friendly front-end interfaces with TypeScript and React to optimize machine uptime, enhance throughput, and reduce resolution time for machine operators.
        \item Managed version control systems to promote effective collaboration, maintain code integrity, and streamline development workflows.
    \end{jobitems}}

\employer
    {Autodesk, Inc.}
    {https://www.autodesk.com}
    {January 2022 --- December 2022}
    {Quality Assurance Engineering Intern}
    {\begin{jobitems}
        \item Created and maintained end-to-end tests for Revit architecture software to ensure reliability and performance.
        \item Collaborated with teammates on an Agile team and used git + GitHub to track progress and maintain version control.
        \item Performed root cause analysis on software bugs, proposed potential solutions, and effectively communicated findings to non-technical employees through release notes and memos.
    \end{jobitems}}

\employer
    {Northeastern University CAMD}
    {https://camd.northeastern.edu}
    {September 2021--- December 2021}
    {Graduate Teaching Assistant}
    {\begin{jobitems}
        \item Instructed and assisted students one-on-one during course meetings and office hours to resolve technical challenges.
        \item Taught students from non-technical backgrounds to gain hands-on experience with JavaScript, Typescript, D3.js, and processing large data sets.
    \end{jobitems}}

\section{Education}

\stdtable{
School     & Northeastern University \hfill Class of 2023\\
Degree     & B.S., Computer Science \& Design\\
GPA        & 3.51/4.00; \emph{cum laude}\\
Coursework & Algorithms, Object Oriented Design, Web Development, Artificial Intelligence, Programming Languages
}

\section{Technical Skills}
\stdtable{
Languages \& Frameworks & Python \centereddot TypeScript \centereddot JavaScript \centereddot React \centereddot SQL \centereddot Java \centereddot HTML + CSS \\
Tools      & Git \centereddot Linux \centereddot Jenkins \centereddot GitHub Actions \centereddot Docker \centereddot Kubernetes\\
}

\section{Projects}
\project
    {Unraveling Babel}
    {https://github.com/paulplew/banned-books}
    {Software Engineer and Designer}
    {Unraveling Babel is a hypothetical art installation that covers the topic of book banning
    and censorship in the United States. While it was not built the installation includes
    bespoke interactive displays, advertising material, and guides for how the layout
    of the installation would look.}

\project
    {Cannery}
    {https://github.com/paulplew/cannery}
    {Type Designer}
    {Cannery is a neo-transitional serif typeface designed for typesetting printed text
    in all forms. The typeface was created as a reference to the work of historical 
    typographers Thomas Baskerville and Pierre Simon Fournier.}

\project
    {Flood Book}
    {https://github.com/paulplew/flood-book}
    {Software Engineer and Designer}
    {Flood book is a piece of experience art that was published on the Chrome web store.
    The aim of the work is to decrease the amount of time a user spends on Facebook. This plugin works by 
    slowly obscuring the Facebook window with a flood, acting as a visual metaphor
    for the way social media floods the mind and changes the way people think.}

\end{document}
